\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{cite}

\title{CSci 8980\\Project - Stick Solo\\Update}
\author{
Yashasvi Sriram Patkuri - patku001@umn.edu\\
}

\begin{document}
\maketitle
\pagebreak

\paragraph{description}
Generate controller for stick-figure agents for the task of rock climbing. Everything 2D.

\paragraph{quick terminology}
NR chain: A serially connected N edges with controllable joint angles.
Has N links, N joint angles ($q_i$s), N + 1 vertices.

\paragraph{baseline}
\begin{enumerate}[nolistsep]
    \item Gradient descent.
        \[
            \Delta q \equiv \frac{\delta (goal - end)^2}{\delta q}
        \]
    \item No constraints on $q_i$s.
    \item No constraints on $\Delta q_i$s.
    \item No center of mass considerations.
    \item No multi-limb coordination.
\end{enumerate}

\paragraph{new}
\begin{enumerate}[nolistsep]
    \item Constraints on $q_i$s.
    \item Constraints on $\Delta q_i$s.
    \item Center of mass considerations.
        \[
            \Delta q \equiv
            \frac{\delta (goal - end)^2}{\delta q}
            +
            \frac{\delta (com_x - com_{x\_goal})^2}{\delta q}
            +
            \frac{\delta com_y}{\delta q}
        \]
    \item 4R as 2 limb. Therefore inherent limb coordination.
    \item Constraints on $q_i$ causes local minima problems with gradient descent.
    \item Solution:
        \begin{enumerate}[nolistsep]
            \item Matching hands.
            \item Relaxing agent (or) Global optimal solve using monte carlo method. No prior vs Prior.
        \end{enumerate}
    \item All asymptotically solve the problem.
\end{enumerate}

\paragraph{next steps}
\begin{enumerate}[nolistsep]
    \item Join two NR chain.
    \item Formulate it as RL problem.
\end{enumerate}

\end{document}
